---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  message = FALSE,
  warning = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ShinyIDEA

<!-- badges: start -->

[![Lifecycle:experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![packageversion](https://img.shields.io/badge/Package%20version-0.1.0-orange?style=flat-square)](commits/master)
[![Licence](https://img.shields.io/badge/licence-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)

<!-- badges: end -->

This repository contains the source code for ShinyIDEA.

ShinyIDEA is a web app aimed at making the tools developed in [{IDEATools}](https://github.com/davidcarayon/IDEATools) available to any user.

The app has been developed following the [{golem}](https://github.com/ThinkR-open/golem) and [ShinyModules](https://shiny.rstudio.com/articles/modules.html) frameworks and has been designed using the [{bs4Dash}](https://rinterface.github.io/bs4Dash/) package.


# Prerequisite

The hosting server should have installed :

- LaTeX (`tinytex::install_tinytex()` should be enough)

- The following R package from Github :

```{r, eval = FALSE}
remotes::install_github("davidcarayon/IDEATools")
remotes::install_github("rstudio/sass")
```

- The following R packages from CRAN :

```{r}
dplyr::filter(rsconnect::appDependencies(), source == "CRAN")
```

